Reanalysis Step 2: Multiple Imputation

### 2025-08-29 reanalysis-2-multiple_imputation.qmd
bugfix

  # Don't let fellow eye variables be predicted by anything
  pred_matrix[c("fellow_outcome_VA", "fellow_baseline_VA", "fellow_intermediate_VA", 
                "fellow_lapsed", "fellow_dr"), ] <- 0

  # Don't let fellow eye variables be their own predictors
  pred_matrix["fellow_outcome_VA", "fellow_outcome_VA"] <- 0
  pred_matrix["fellow_baseline_VA", "fellow_baseline_VA"] <- 0
  pred_matrix["fellow_intermediate_VA", "fellow_intermediate_VA"] <- 0
}

# Patient-level variables can predict eye-level outcomes (but not strongly)
if ("patient_worst_baseline" %in% colnames(pred_matrix)) {
  pred_matrix[, "patient_worst_baseline"] <- 1
  pred_matrix[, "patient_best_baseline"] <- 1
  pred_matrix[, "patient_ever_lapsed"] <- 1

  # But don't predict these variables
  pred_matrix["patient_worst_baseline", ] <- 0
  pred_matrix["patient_best_baseline", ] <- 0
  pred_matrix["patient_ever_lapsed", ] <- 0
}

# n_eyes and has_fellow are just indicators, not predictors
if ("n_eyes" %in% colnames(pred_matrix)) {
  pred_matrix[, "n_eyes"] <- 0
  pred_matrix["n_eyes", ] <- 0
  pred_matrix[, "has_fellow"] <- 0
  pred_matrix["has_fellow", ] <- 0
}

>>>>

  # Don't let fellow eye variables be predicted by anything
  # Only set for variables that actually exist in the matrix
  fellow_vars_in_matrix <- c("fellow_outcome_VA", "fellow_baseline_VA", "fellow_intermediate_VA", "fellow_dr")
  fellow_vars_in_matrix <- fellow_vars_in_matrix[fellow_vars_in_matrix %in% rownames(pred_matrix)]
  if (length(fellow_vars_in_matrix) > 0) {
    pred_matrix[fellow_vars_in_matrix, ] <- 0
  }

  # Don't let fellow eye variables be their own predictors
  if ("fellow_outcome_VA" %in% rownames(pred_matrix)) {
    pred_matrix["fellow_outcome_VA", "fellow_outcome_VA"] <- 0
  }
  if ("fellow_baseline_VA" %in% rownames(pred_matrix)) {
    pred_matrix["fellow_baseline_VA", "fellow_baseline_VA"] <- 0
  }
  if ("fellow_intermediate_VA" %in% rownames(pred_matrix)) {
    pred_matrix["fellow_intermediate_VA", "fellow_intermediate_VA"] <- 0
  }
}

# Patient-level variables can predict eye-level outcomes (but not strongly)
if ("patient_worst_baseline" %in% colnames(pred_matrix)) {
  pred_matrix[, "patient_worst_baseline"] <- 1
  pred_matrix[, "patient_best_baseline"] <- 1
  # pred_matrix[, "patient_ever_lapsed"] <- 1  # REMOVED - variable not in imputation

  # But don't predict these variables
  pred_matrix["patient_worst_baseline", ] <- 0
  pred_matrix["patient_best_baseline", ] <- 0
  # pred_matrix["patient_ever_lapsed", ] <- 0  # REMOVED - variable not in imputation
}

# n_eyes is just an indicator, not a predictor
if ("n_eyes" %in% colnames(pred_matrix)) {
  pred_matrix[, "n_eyes"] <- 0
  pred_matrix["n_eyes", ] <- 0
  # has_fellow removed from imputation - was collinear with n_eyes
}
